### 2020-08-26 benchmarking/benchmarkingVM/ESS_round3.tex
results update

% Created by tikzDevice version 0.12.3 on 2020-08-10 15:55:24
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 76.35) --
	(212.73,289.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.35,289.08) --
	(271.35,195.00) --
	( 76.35,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 50.90) --
	(238.18,289.08);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.35,289.08) --
	(271.35,220.45) --
	( 50.90,  0.00);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 25.45) --
	(263.63,289.08);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (271.35,289.08) --
	(271.35,245.90) --
	( 25.45,  0.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (145.42, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,150.12) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (119.97, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,124.67) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.53, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 99.22) {$4\times$};

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.97,173.04) --
	(174.56,173.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.02,163.26) --
	(170.02,179.39);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.02,169.15) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.16,172.12) --
	(172.25,172.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.32,170.07) --
	(170.32,173.96);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.32,167.26) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.73,184.48) --
	(183.91,184.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.85,183.02) --
	(182.85,185.84);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.85,179.62) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.83,152.06) --
	(151.70,152.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.43,146.58) --
	(145.43,156.28);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (145.43,147.20) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.34,176.95) --
	(176.22,176.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.31,171.72) --
	(172.31,181.01);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (172.31,173.45) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.52,189.61) --
	(189.61,189.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.07,189.39) --
	(189.07,189.83);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.07,186.11) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.89,177.49) --
	(176.50,177.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.34,177.31) --
	(174.34,177.66);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.34,173.60) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.00,179.60) --
	(179.72,179.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.96,177.03) --
	(177.96,181.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.96,174.74) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.92,182.73) --
	(183.11,182.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.02,182.56) --
	(183.02,182.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.02,177.87) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.08,144.73) --
	(143.52,144.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.58,137.44) --
	(140.58,149.93);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (140.58,139.87) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.53,157.68) --
	(164.32,157.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.84,139.80) --
	(160.84,166.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (160.84,154.18) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.53,191.09) --
	(191.56,191.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.05,190.40) --
	(191.05,191.75);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.05,187.59) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.25,170.79) --
	(183.76,170.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.21,169.12) --
	(181.21,172.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.21,166.90) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.52,175.16) --
	(188.36,175.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.10,159.21) --
	(182.10,183.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.10,170.30) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.87,190.74) --
	(190.95,190.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.41,189.74) --
	(190.41,191.69);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.41,185.88) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.08,153.71) --
	(157.42,153.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.97,149.99) --
	(152.97,156.80);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.97,148.85) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.95,170.40) --
	(184.11,170.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.10,167.27) --
	(180.10,173.07);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.10,166.90) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.12,201.71) --
	(203.34,201.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.27,200.95) --
	(202.27,202.44);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (202.27,198.21) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08, 60.00);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,102.27) -- ( 54.00,102.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,144.54) -- ( 54.00,144.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,186.81) -- ( 54.00,186.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,229.08) -- ( 54.00,229.08);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 98.83) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,141.10) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,183.37) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,225.64) {10000};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,109}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:33:46
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00, 71.00) --
	(218.08,289.08);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (268.39,289.08) --
	(268.39,197.39) --
	( 71.00,  0.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 47.34) --
	(241.74,289.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.39,289.08) --
	(268.39,221.06) --
	( 47.34,  0.00);

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00, 23.67) --
	(265.41,289.08);

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (268.39,289.08) --
	(268.39,244.72) --
	( 23.67,  0.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.08, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,144.78) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.41, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,121.11) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 90.75, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 97.44) {$4\times$};

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.17,196.99) --
	(201.72,196.99);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.96,196.43) --
	(200.96,197.53);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.96,193.10) {$p$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.11,198.75) --
	(207.67,198.75);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.44,197.10) --
	(206.44,200.25);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.44,193.89) {$L$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.83,203.06) --
	(206.19,203.06);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.01,202.94) --
	(206.01,203.18);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.01,198.20) {$r$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.99,182.32) --
	(180.78,182.32);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.91,181.55) --
	(179.91,183.06);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.91,177.46) {$h$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.73,181.94) --
	(183.35,181.94);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.20,181.15) --
	(181.20,182.69);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.20,178.44) {$\sigma$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.29,207.61) --
	(213.84,207.61);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.08,206.84) --
	(213.08,208.35);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (213.08,204.11) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (217.25, 60.00);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.31) -- ( 54.00, 99.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,138.62) -- ( 54.00,138.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,177.93) -- ( 54.00,177.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,217.25) -- ( 54.00,217.25);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.87) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,135.18) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,174.49) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,213.80) {10000};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,109}
